О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
The last language issue

Basing on the exact values of $d(2,n)$ for $ 3 \leq n\leq 122$ and the estimate $d(2,123)>10000$
\cite{kurz2008bounds}, we derive
\begin{proposition}
	\label{obs:4_leq_n_leq_21491}
	The inequality
	\begin{equation}
		d(2,n) \geq 3^{1/4}\cdot2^{-3/2} \cdot n
	\end{equation}
	holds for $4 \leq n \leq 21491$.
\end{proposition}

@@

Performing some simple manipulations with the upper bound in Theorem~\ref{thm:varphi_k_bounds},
one can make the following
\begin{proposition}
	\label{varphi_n_where_n_geq_21492}
	For $n \geq 21492$ we have
	\begin{equation}
		\varphi_n \leq \varphi_{n-1} \leq \frac{\beta}{\sqrt{n-2}}
		,
	\end{equation}
	where
	\begin{equation}
		\beta = \frac{1}{\sqrt{21490}} + \sqrt{ \frac{2}{\sqrt{3}} + \frac{1}{21490} } < 1.07464
		.
	\end{equation}
\end{proposition}

Now we need to estimate the quanity of points in an intersection of an integral point set with a line segment.
There is the following estimate for minimum diameter of planar integral point sets with many collinear points:
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
However, the estimate is rather unsuitable for our needs,
as it does not provide the values of all the constants.
To obtain the desired estimate, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

@@

We can improve the constant in Theorem~\ref{thm:main_estimate},
if some new exact values of $d(2,n)$ are found;
however, the obtained constant is bounded by $3^{1/4}\cdot2^{-3/2}$.
To be precise, we have the following

@@

To describe all the sets $M \in \mathfrak{M}(2,n)$ with distance 1,
we will need~\cite[Proposition 6]{our-vmmsh-2018}.
For the sake of completeness, we will give here a slightly rephrased version of it with the proof as
\begin{lemma}
	\label{lem:no_4_points_in_semigeneral_position_with_distance_1}
	Let $M=\{M_1,M_2,M_3,M_4\}\in \mathfrak{M}(2,4)$ such that $|M_1 M_2|=1$
	and let $l$ be the straight line containing points $M_1$ and $M_2$.
	Then one of the points $M_3$ or $M_4$ belongs to $l$.
\end{lemma}

@@

Using Construction~\ref{con:planar_set_with_minimeter_1},
Lemma~\ref{lem:no_4_points_in_semigeneral_position_with_distance_1} and Corollary~\ref{cor:only_one_distance_1_on_straight_line}
together with results of~\cite[Section 6]{antonov2008maximal},
we obtain the following

@@

Using the ``blowing up'' procedure described in~\cite[theorem 1.3]{kurz2008bounds},
we can construct an integral point set $M$ in $m$-dimensional Euclidean space, $m\geq 3$,
with distance 1 occuring in it.
If we have an integral point set with distance 1 occuring,
then we can easily dilate it to turn 1 into the desired distance.
These facts, together with Theorem~\ref{thm:minimeter_1_planar}, give the following

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $M$
	not more than $1+\frac{(m-1)^2 - (m-1)}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-2)$-dimensional simplex.

@@

\section{Language issues to be resolved before publication}

\begin{enumerate}
	\item
		... the following \\ Theorem X.

		is it correct to split the sentence in such a way?
		We should avoid it if possible.
\end{enumerate}

>>>>

Basing on the exact values of $d(2,n)$ for $ 3 \leq n\leq 122$ and the estimate $d(2,123)>10000$
\cite{kurz2008bounds}, we derive the following proposition.
\begin{proposition}
	\label{obs:4_leq_n_leq_21491}
	The inequality
	\begin{equation}
		d(2,n) \geq 3^{1/4}\cdot2^{-3/2} \cdot n
	\end{equation}
	holds for $4 \leq n \leq 21491$.
\end{proposition}

@@

Performing some simple manipulations with the upper bound in Theorem~\ref{thm:varphi_k_bounds},
one can make the following proposition.
\begin{proposition}
	\label{varphi_n_where_n_geq_21492}
	For $n \geq 21492$ we have
	\begin{equation}
		\varphi_n \leq \varphi_{n-1} \leq \frac{\beta}{\sqrt{n-2}}
		,
	\end{equation}
	where
	\begin{equation}
		\beta = \frac{1}{\sqrt{21490}} + \sqrt{ \frac{2}{\sqrt{3}} + \frac{1}{21490} } < 1.07464
		.
	\end{equation}
\end{proposition}

Now we need to estimate the quanity of points in an intersection of an integral point set with a line segment.
There is the following estimate for minimum diameter of planar integral point sets with many collinear points.
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 \log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
However, the estimate is rather unsuitable for our needs,
as it does not provide the values of all the constants.
To obtain the desired estimate, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

@@

We can improve the constant in Theorem~\ref{thm:main_estimate},
if some new exact values of $d(2,n)$ are found;
however, the obtained constant is bounded by $3^{1/4}\cdot2^{-3/2}$.
To be precise, we have the following theorem.

@@

To describe all the sets $M \in \mathfrak{M}(2,n)$ with distance 1,
we will need~\cite[Proposition 6]{our-vmmsh-2018}.
For the sake of completeness, we will give here a slightly rephrased version of it with the proof as the following lemma.
\begin{lemma}
	\label{lem:no_4_points_in_semigeneral_position_with_distance_1}
	Let $M=\{M_1,M_2,M_3,M_4\}\in \mathfrak{M}(2,4)$ such that $|M_1 M_2|=1$
	and let $l$ be the straight line containing points $M_1$ and $M_2$.
	Then one of the points $M_3$ or $M_4$ belongs to $l$.
\end{lemma}

@@

Using Construction~\ref{con:planar_set_with_minimeter_1},
Lemma~\ref{lem:no_4_points_in_semigeneral_position_with_distance_1} and Corollary~\ref{cor:only_one_distance_1_on_straight_line}
together with results of~\cite[Section 6]{antonov2008maximal},
we obtain the following theorem.

@@

Using the ``blowing up'' procedure described in~\cite[theorem 1.3]{kurz2008bounds},
we can construct an integral point set $M$ in $m$-dimensional Euclidean space, $m\geq 3$,
with distance 1 occuring in it.
If we have an integral point set with distance 1 occuring,
then we can easily dilate it to turn 1 into the desired distance.
These facts, together with Theorem~\ref{thm:minimeter_1_planar}, give the following theorem.

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward the following conjecture.
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $M$
	not more than $1+\frac{(m-1)^2 - (m-1)}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-2)$-dimensional simplex.

@@
